Trifunctional Sphingosine

### 2025-02-23 IndividualStudies/AT_2025.qmd
Pre-rendering GO analysis so rendering is faster

AT_2025_Long <- readr::read_csv("DataTables/AT_ChemicalCommunications_2025_download.csv")

@@

>>>>

AT_2025_Long <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/AT_ChemicalCommunications_2025_download.csv"))

@@

## Gene Ontology enrichment

**In beta: GO analysis still under development**

#### Cell Compartment

:::{.border}
```{r, echo=FALSE, warning=FALSE}
# #### These functions make the plots to be displayed in this div - uncomment them to run them again
# CC_enrichment_plots(AT_2025_Long, "dot", "PE-PA_AT_2025_CC-DOTplot")
# CC_enrichment_plots(AT_2025_Long, "cnet", "PE-PA_AT_2025_CC-CNETplot")
```

<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>

![](/IndividualStudies/GO_plots/PE-PA_AT_2025_CC-CNETplot.png)

#### Molecular Function

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# MF_enrichment_plots(AT_2025_Long, "dot", "PE-PA_AT_2025_MF-DOTplot")
# MF_enrichment_plots(AT_2025_Long, "cnet", "PE-PA_AT_2025_MF-CNETplot")
```

<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>

![](/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-CNETplot.png)

#### Biological Process

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# BP_enrichment_plots(AT_2025_Long, "dot", "PE-PA_AT_2025_BP-DOTplot")
# BP_enrichment_plots(AT_2025_Long, "cnet", "PE-PA_AT_2025_BP-CNETplot")
```

<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>

![](/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-CNETplot.png)

### 2025-02-23 IndividualStudies/SF_2024.qmd
Pre-rendering GO analysis so rendering is faster

# Opening the datatable for this page IN FINAL RENDER
SF_2024_data <- readr::read_csv("DataTables/SF_ACS-Chem-Bio_2024_download.csv")

@@

suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
```
:::

@@

suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))

@@

suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))

>>>>

# Opening the datatable for this page IN FINAL RENDER
SF_2024_data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
# #### These functions make the plots to be displayed in this div - uncomment them to run them again
# CC_enrichment_plots(SF_2024_data, "dot", "/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-DOTplot")
# CC_enrichment_plots(SF_2024_data, "cnet", "/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-CNETplot")
```

<iframe src="/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>

![](/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-CNETplot.png)

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# MF_enrichment_plots(SF_2024_data, "dot", "/IndividualStudies/GO_plots/Sph-Spa_SF_2024_MF-DOTplot")
# MF_enrichment_plots(SF_2024_data, "cnet", "/IndividualStudies/GO_plots/Sph-Spa_SF_2024_MF-CNETplot")
```

<iframe src="/IndividualStudies/GO_plots/Sph-Spa_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>

(MF CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# BP_enrichment_plots(SF_2024_data, "dot", "/IndividualStudies/GO_plots/Sph-Spa_SF_2024_BP-DOTplot")
# BP_enrichment_plots(SF_2024_data, "cnet", "/IndividualStudies/GO_plots/Sph-Spa_SF_2024_BP-CNETplot")
```

(No BP pathways identified among enriched hits and candidates.)

(BP CNET plot failed in production)
:::

### 2025-02-23 IndividualStudies/SF_2024_B.qmd
Pre-rendering GO analysis so rendering is faster

# Opening the datatable for this page IN FINAL RENDER
SF_2024_data <- readr::read_csv(paste0(here(), "/IndividualStudies//DataTables/SF_Chem_Comm_2024_download.csv"))

@@

suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
```
:::

@@

suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))

@@

suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))

>>>>

# Opening the datatable for this page IN FINAL RENDER
SF_2024_data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_Chem_Comm_2024_download.csv"))

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
# #### These functions make the plots to be displayed in this div - uncomment them to run them again
# CC_enrichment_plots(SF_2024_data, "dot", "/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-DOTplot")
# CC_enrichment_plots(SF_2024_data, "cnet", "/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-CNETplot")
```

<iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>

![](/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-CNETplot.png)

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# MF_enrichment_plots(SF_2024_data, "dot", "/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_MF-DOTplot")
# MF_enrichment_plots(SF_2024_data, "cnet", "/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_MF-CNETplot")
```

<iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>

(MF CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# BP_enrichment_plots(SF_2024_data, "dot", "/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_BP-DOTplot")
# BP_enrichment_plots(SF_2024_data, "cnet", "/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_BP-CNETplot")
```

<iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_BP-DOTplot.html" width="100%" height="500px"></iframe>

(BP CNET plot failed in production)
:::

### 2025-02-23 LipidProbe/1-10_FattyAcid.qmd
Pre-rendering GO analysis so rendering is faster

<!-- R setup, reading dataframes and minor data wrangling -->
```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(htmltools)

## Opening the source file for the ggplot custom theme
source("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/Resources/ggplot_styles.R")

@@

# Opening the datatable for this page
SF_2024_data <- readr::read_csv("DataSets/1-10_FA_Huh7_SF_2024.csv") |>
	filter(LipidProbe == "1-10 FA")

@@

suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
```
:::

@@

suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))

@@

suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))

>>>>

<!-- R setup, reading dataframes and minor data wrangling -->
```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(htmltools)
library(here)

## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))

@@

# Opening the datatable for this page
SF_2024_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")) |>
	filter(LipidProbe == "1-10 FA")

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
# #### These functions make the plots to be displayed in this div - uncomment them to run them again
# CC_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/1-10FA_SF_2024_CC-DOTplot")
# CC_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/1-10FA_SF_2024_CC-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/1-10FA_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>

(CC CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# MF_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/1-10FA_SF_2024_MF-DOTplot")
# MF_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/1-10FA_SF_2024_MF-CNETplot")
```

(No MF pathways identified among enriched hits and candidates.)

(MF CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# BP_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/1-10FA_SF_2024_BP-DOTplot")
# BP_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/1-10FA_SF_2024_BP-CNETplot")
```

(No BP pathways identified among enriched hits and candidates.)

(BP CNET plot failed in production)
:::
:::

### 2025-02-23 LipidProbe/8-3_FattyAcid.qmd
Pre-rendering GO analysis so rendering is faster

# Opening the datatable for this page
SF_2024_data <- readr::read_csv("DataSets/8-3_FA_Huh7_SF_2024.csv") |>
	filter(LipidProbe == "8-3 FA")

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
```
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))

>>>>

# Opening the datatable for this page
SF_2024_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")) |>
	filter(LipidProbe == "8-3 FA")

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
# #### These functions make the plots to be displayed in this div - uncomment them to run them again
# CC_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/8-3FA_SF_2024_CC-DOTplot")
# CC_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/8-3FA_SF_2024_CC-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/8-3FA_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>

(CC CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# MF_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/8-3FA_SF_2024_MF-DOTplot")
# MF_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/8-3FA_SF_2024_MF-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/8-3FA_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>

(MF CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# BP_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/8-3FA_SF_2024_BP-DOTplot")
# BP_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/8-3FA_SF_2024_BP-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/8-3FA_SF_2024_BP-DOTplot.html" width="100%" height="500px"></iframe>

(BP CNET plot failed in production)
:::
:::

### 2025-02-23 LipidProbe/PhosphatidicAcid.qmd
Minor changes
Pre-rendering GO analysis so rendering is faster

---
title: "Trifunctional Phosphatidic Acid"
prefer-html: true
---

@@

AT_2025_Long <- readr::read_csv("DataSets/PA_HeLa_AT_2025.csv")

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(CC_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(CC_enrichment_plots(AT_2025_Long, "cnet"))
```
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(MF_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(MF_enrichment_plots(AT_2025_Long, "cnet"))

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(BP_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(BP_enrichment_plots(AT_2025_Long, "cnet"))

```
:::
:::

>>>>

---
title: "Trifunctional Phosphatidic Acid"
prefer-html: true
format:
  html: default

---

@@

AT_2025_Long <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv"))

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
# #### These functions make the plots to be displayed in this div - uncomment them to run them again
# CC_enrichment_plots(AT_2025_Long, "dot", "/LipidProbe/GO_plots/PA_AT_2025_CC-DOTplot")
# CC_enrichment_plots(AT_2025_Long, "cnet", "/LipidProbe/GO_plots/PA_AT_2025_CC-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/PA_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>

(CC CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# MF_enrichment_plots(AT_2025_Long, "dot", "/LipidProbe/GO_plots/PA_AT_2025_MF-DOTplot")
# MF_enrichment_plots(AT_2025_Long, "cnet", "/LipidProbe/GO_plots/PA_AT_2025_MF-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>

(MF CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# BP_enrichment_plots(AT_2025_Long, "dot", "/LipidProbe/GO_plots/PA_AT_2025_BP-DOTplot")
# BP_enrichment_plots(AT_2025_Long, "cnet", "/LipidProbe/GO_plots/PA_AT_2025_BP-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/PA_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>

(BP CNET plot failed in production)
:::
:::

### 2025-02-23 LipidProbe/Phosphatidylethanolamine.qmd
Minor changes
Pre-rendering GO analysis so rendering is faster

---
title: "Trifunctional Phosphatidylethanolamine"
prefer-html: true
---

@@

AT_2025_Long <- readr::read_csv("DataSets/PE_HeLa_AT_2025.csv")

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(CC_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(CC_enrichment_plots(AT_2025_Long, "cnet"))
```
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(MF_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(MF_enrichment_plots(AT_2025_Long, "cnet"))

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}

suppressMessages(BP_enrichment_plots(AT_2025_Long, "dot"))

suppressMessages(BP_enrichment_plots(AT_2025_Long, "cnet"))

>>>>

---
title: "Trifunctional Phosphatidylethanolamine"
prefer-html: true
format:
  html: default

---

@@

AT_2025_Long <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/PE_HeLa_AT_2025.csv"))

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
# #### These functions make the plots to be displayed in this div - uncomment them to run them again
# CC_enrichment_plots(AT_2025_Long, "dot", "/LipidProbe/GO_plots/PE_AT_2025_CC-DOTplot")
# CC_enrichment_plots(AT_2025_Long, "cnet", "/LipidProbe/GO_plots/PE_AT_2025_CC-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/PE_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>

(CC CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# MF_enrichment_plots(AT_2025_Long, "dot", "/LipidProbe/GO_plots/PE_AT_2025_MF-DOTplot")
# MF_enrichment_plots(AT_2025_Long, "cnet", "/LipidProbe/GO_plots/PE_AT_2025_MF-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/PE_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>

(MF CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# BP_enrichment_plots(AT_2025_Long, "dot", "/LipidProbe/GO_plots/PE_AT_2025_BP-DOTplot")
# BP_enrichment_plots(AT_2025_Long, "cnet", "/LipidProbe/GO_plots/PE_AT_2025_BP-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/PE_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>

(BP CNET plot failed in production)
:::
:::

### 2025-02-23 LipidProbe/Sphinganine.qmd
Pre-rendering GO analysis so rendering is faster

---
title: "Trifunctional sphinganine"
prefer-html: true
---

@@

# Opening the datatable for this page
SF_2024_data <- readr::read_csv("DataSets/Spa_Huh7_SF_2024.csv") |>
	filter(LipidProbe == "Spa")

@@

suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
```
:::

@@

suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))

@@

suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))

>>>>

---
title: "Trifunctional sphinganine"
prefer-html: true
format: html
---

@@

# Opening the datatable for this page
SF_2024_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv")) |>
	filter(LipidProbe == "Spa")

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
# #### These functions make the plots to be displayed in this div - uncomment them to run them again
# CC_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/Spa_SF_2024_CC-DOTplot")
# CC_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/Spa_SF_2024_CC-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/Spa_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>

(CC CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# MF_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/Spa_SF_2024_MF-DOTplot")
# MF_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/Spa_SF_2024_MF-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/Spa_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>

(MF CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# BP_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/Spa_SF_2024_BP-DOTplot")
# BP_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/Spa_SF_2024_BP-CNETplot")
```

(No BP pathways identified among enriched hits and candidates.)

(BP CNET plot failed in production)
:::
:::

### 2025-02-23 LipidProbe/Sphingosine.qmd
Pre-rendering GO analysis so rendering is faster

# Opening the datatable for this page
SF_2024_data <- readr::read_csv("DataSets/Sph_Huh7_SF_2024.csv") |>
	filter(LipidProbe == "Sph")

@@

# Applies the ID column to the Spa results
SF_2024_ranked <- SF_2024_data |>
    arrange(logFC) |>
	filter(LipidProbe == "Sph") |>
	mutate(ID = ID)

@@

suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
```
:::

@@

suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))

@@

suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))

suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))

>>>>

# Opening the datatable for this page
SF_2024_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")) |>
	filter(LipidProbe == "Sph")

@@

# Applies the ID column to the Sph results
SF_2024_ranked <- SF_2024_data |>
    arrange(logFC) |>
	filter(LipidProbe == "Sph") |>
	mutate(ID = ID)

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
# #### These functions make the plots to be displayed in this div - uncomment them to run them again
# CC_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_CC-DOTplot")
# CC_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_CC-CNETplot")
```

<iframe src="/LipidProbe/GO_plots/Sph_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>

(CC CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# MF_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_MF-DOTplot")
# MF_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_MF-CNETplot")
```

(No MF pathways identified among enriched hits and candidates.)

(MF CNET plot failed in production)
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# BP_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_BP-DOTplot")
# BP_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_BP-CNETplot")
```

(No BP pathways identified among enriched hits and candidates.)

(BP CNET plot failed in production)
:::
:::
